Ages of Planets and Stars Observed by Kepler

### 2024-04-04 paper/ms.tex
minor

In terms of actual detected planet counts, our rotation-based ages for
the Kepler sample yield \{\nplyounggyro, \nplmidgyro, \nploldgyro\}
detected planets in the 0-1\,Gyr, 1-2\,Gyr, and 2-3\,Gyr bins.
For the sub-gigayear bin in particular, which holds specific weight in
studies of planet evolution, while there are \nplyounggyro\ planets
with median ages below 1\,Gyr, if we were to require $t_{\rm
gyro}$$<$1\,Gyr at 2$\sigma$ confidence, this would leave only
\nplyounggyrotwosigma\ planets orbiting \nplhostsyounggyrotwosigma\
stars.

\subsection{Sanity Checks}
To date, four stellar clusters in the Kepler field have fielded planet
detections.
They are:...
Young Kepler systems with the most precisely measured ages are...

>>>>

In terms of detected planet counts, our rotation-based ages for
the Kepler sample yield \{\nplyounggyro, \nplmidgyro, \nploldgyro\}
detected planets in the 0-1\,Gyr, 1-2\,Gyr, and 2-3\,Gyr bins.
For the sub-gigayear bin in particular, which holds specific weight in
studies of planet evolution, while there are \nplyounggyro\ planets
with median ages below 1\,Gyr, requiring $t_{\rm
gyro}$$<$1\,Gyr at 2$\sigma$ confidence yields
\nplyounggyrotwosigma\ planets orbiting \nplhostsyounggyrotwosigma\
stars.

\subsection{Sanity Checks}
To date, four stellar clusters in the Kepler field have yielded planet
detections.
They are:...
Young Kepler systems with the most precisely measured ages are...
